---
title: "TFM"
output: html_document
date: "2025-03-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

```{r}
rm(list = ls())
library(tidyverse)
library(readxl)
library(DataExplorer)
```

# ERDF expenditure data

## Loading data

```{r}
funds <- read_csv("funds.csv")

funds <- funds |>
  # Selecting only ERDF data
  filter(Fund == "ERDF") |> 
  # Selecting only relevant variables
  select(Country, NUTS2_ID, NUTS2_name, Year, 
         Programming_Period, Modelled_annual_expenditure) |> 
  rename(Budget_Cycle = Programming_Period,
         Expenditure = Modelled_annual_expenditure)
```

As per source this expenditure data uses NUTS 2013 codes

## Cleaning

```{r}
funds <- funds |> 
  # Pivoting wider to obtain 1 column per budget period
  pivot_wider(names_from = Budget_Cycle, values_from = Expenditure,
              names_glue = "expenditure_{Budget_Cycle}_budget") |> 
  arrange(NUTS2_ID, Year) 

# Getting rid of years before 1989 as the budget periods covered start in 1989
funds <- funds |> 
  filter(Year >= 1989)
```

Checking that the NUTS codes used in the expenditure data are in line with the official 2013 NUTS codes

```{r}
# Loading the NUTS code (changes from 2013 to 2016 codes)
NUTS13_16 <- read_excel("NUTS2013-NUTS2016.xlsx", 
                        sheet = "NUTS2013-NUTS2016", range = "B2:I1868")

# # Optionally loading NUTS codes using changes from 2010 to 2013 (just to check coherence with 13-16 data)
# NUTS10_13 <- read_excel("NUTS 2010 - NUTS 2013.xls",
#                         sheet = "NUTS2010-NUTS2013", range = "B2:L1918")

NUTS_2013 <- NUTS13_16 |> 
  # Selecting only level 2 regions
  filter(level==2) |> 
  # Keeping only regions with a 2013 NUTS code
  drop_na(`Code 2013`) |> 
  # Selecting only relevant variables
  select(`Code 2013`, `NUTS level 2`)

# Storing all NUTS used in the expenditure data and in the 2013 official codes
nuts_funded <- unique(funds$NUTS2_ID) 
all_nuts <- unique(NUTS_2013$`Code 2013`)

# Codes that are in the funds dataset but are not 2013 nuts code
setdiff(nuts_funded, all_nuts)
```

Fixing those codes (they are primarily due to ...)

```{r}
funds <- funds |> 
  # Greece
  mutate(NUTS2_ID = case_when(
    NUTS2_ID == "EL11" ~ "EL51",
    NUTS2_ID == "EL12" ~ "EL52",
    NUTS2_ID == "EL13" ~ "EL53",
    NUTS2_ID == "EL14" ~ "EL61",
    NUTS2_ID == "EL21" ~ "EL54",
    NUTS2_ID == "EL22" ~ "EL62",
    NUTS2_ID == "EL23" ~ "EL63",
    NUTS2_ID == "EL24" ~ "EL64",
    NUTS2_ID == "EL25" ~ "EL65",
    TRUE ~ NUTS2_ID
  )) |> 
  # Slovenia
  mutate(NUTS2_ID = case_when(
    NUTS2_ID == "SI01" ~ "SI03",
    NUTS2_ID == "SI02" ~ "SI04",
    TRUE ~ NUTS2_ID
  )) |> 
  # France
  mutate(NUTS2_ID = case_when(
    NUTS2_ID == "FR91" ~ "FRA1",
    NUTS2_ID == "FR92" ~ "FRA2",
    NUTS2_ID == "FR93" ~ "FRA3",
    NUTS2_ID == "FR94" ~ "FRA4",
    TRUE ~ NUTS2_ID
  ))

# UK is London (seems like funds use 2010 NUTS code instead of 2013)
# This can't be fixed for now as they have split up in more than 1 region UK1->UK3+UK4 and UK2->UK5+UK6+UK7

#Checking
nuts_funded <- unique(funds$NUTS2_ID) 
all_nuts <- unique(NUTS_2013$`Code 2013`)
setdiff(nuts_funded, all_nuts)
```

The remaining NUTS codes from the `funds` dataset that are not official 2013 NUTS codes are UKI1 and UKI2, which as mentioned before are from London and cannot be fixed right now.

I'll now run another check to understand which 2013 NUTS code do not appear at all in my `funds` dataset:

```{r}
setdiff(all_nuts, nuts_funded) 
# Only ZZ plus the regions created from UKI1, UKI2 in 2013 changes

# removing the only ZZ present in funds
funds <- funds |> 
  filter(!NUTS2_ID == "UKZZ")
```

Checking that each region has the correct name

```{r}
# There are some discrepancies, each NUTS2_ID should have its corresponding name
length(unique(funds$NUTS2_ID))
length(unique(funds$NUTS2_name))

# Count the pairs and understand which are the NUTS2_names that are duplicates
counted <- funds |> group_by(NUTS2_ID, NUTS2_name) |> count() |> ungroup()
# Checking which NUTS2_ID have the same name
duplicates <- counted |>  count(NUTS2_name) |> filter(n>1)
duplicates

dup <- funds |> filter(NUTS2_name == "Zahodna Slovenija")
unique(dup$NUTS2_ID)
unique(dup$NUTS2_name)
# SI03 NUTS2_name must be changed to Vzhodna Slovenija from Zahodna Slovenija
# SI04 NUTS2_name should remain Zahodna Slovenija

funds <- funds |> 
  mutate(NUTS2_name = case_when(
    NUTS2_ID == "SI03" ~ "Vzhodna Slovenija",
    NUTS2_ID == "SI04" ~ "Zahodna Slovenija",
    TRUE ~ NUTS2_name
  ))

counted <- funds |> group_by(NUTS2_ID, NUTS2_name) |> count() |> ungroup()
duplicates <- counted |>  count(NUTS2_name) |> filter(n>1)
duplicates
```

Now I have to make sure that each row is a region in a particular year, i.e. each region should only have one row per year (no multiple rows per year). 

Note that for those regions which had some problems above I definitely will have to collapse some rows together. 

```{r}
counted |> arrange(desc(n)) |> head()
# There are some regions that have more than 34 observations (which are the most since data spans from 1989 to 2022)
# This is due to the changes to the nuts code I have made above

# Checking which of the regions are duplicates
duplicates <- funds |> group_by(NUTS2_ID, NUTS2_name, Year) |> 
  count() |> 
  ungroup() |> 
  filter(n>1)
duplicates
# Only the ones that needed help before are duplicates

funds |> 
  filter(NUTS2_ID %in% duplicates$NUTS2_ID & Year %in% duplicates$Year) |> 
  arrange(NUTS2_ID, Year)
# No need to do anything special because there is no overlapping of data, just need to collapse all the data in one row

funds <- funds |> 
  # Summing the expenditure per year and region
  summarise(across(starts_with("expenditure"), ~ sum(.x, na.rm = TRUE)), 
            .by = c(Country, NUTS2_ID, NUTS2_name, Year)) |> 
  # Turning all the 0s cerated by the operation above into NAs
  mutate(across(starts_with("expenditure"), ~ ifelse(.x == 0, NA, .x)))
```

Making sure that each region is present for all the years that needs to be present

```{r}
# Counting the number of countries per year
# They should be:
# 1989-1994 = 12
# 1995-2003 = 15
# 2004-2006 = 25
# 2007-2012 = 27
# 2013 onward = 28
funds |> 
  group_by(Year) |> 
  summarise(n_countries = n_distinct(Country))

# Counting the number of regions
funds |> 
  group_by(Year) |> 
  summarise(n_regions = n_distinct(NUTS2_ID))
```

As some regions are not there even in years where they should be (showed by the fluctuating number of regions/countries per year)

```{r}
# Making sure all regions from the 1990 are also in 1989

# Looking at the differences between the vectors of unique values
NUTS_1989 <- funds |> filter(Year == 1989) |> pull(NUTS2_ID) |> unique()
NUTS_1990 <- funds |> filter(Year == 1990) |> pull(NUTS2_ID) |> unique()
missing_1989 <- setdiff(NUTS_1990, NUTS_1989)
missing_1989

# Creating appropriate data for the missing regions
missing_1989 <- funds |> 
  filter(NUTS2_ID %in% missing_1989) |> 
  filter(Year == 1990) |> 
  mutate(Year = 1989,
         "expenditure_1989-1993_budget"= 0)
funds <- funds |> 
  rbind(missing_1989) |> 
  arrange(NUTS2_ID, Year)
```

```{r}
# Looking at the '95 enlargement
NUTS_1993 <- funds |> filter(Year == 1993) |> pull(NUTS2_ID) |> unique()
NUTS_1994 <- funds |> filter(Year == 1994) |> pull(NUTS2_ID) |> unique()
missing <- setdiff(NUTS_1994, NUTS_1993)
# This should not be there as they were not in the EU before 1995
# This likely happens because of the modelling of the expenditure

# For the countries that join the EU in 1995 I want all expenditure to be in 1995
# Create a df storing their data
df <- funds |>
  filter(Country %in% c("AT", "FI", "SE") & Year == 1994)
# Filtering them out of the main df
funds <- funds |>
  filter(!(Country %in% c("AT", "FI", "SE") & Year == 1994))
# Modifying and adding that data to the main df for year 1995
df <- df |> 
  mutate(Year = 1995) |> 
  select(Country, NUTS2_ID, NUTS2_name, Year, `expenditure_1994-1999_budget`) |> 
  rename("exp_to_be_added" = `expenditure_1994-1999_budget`)
funds <- funds |> 
  left_join(df, by = c("Country", "NUTS2_ID", "NUTS2_name", "Year")) |> 
  mutate(`expenditure_1994-1999_budget` = 
           rowSums(across(c(`expenditure_1994-1999_budget`, exp_to_be_added)), 
                   na.rm = TRUE)) |> 
  select(-exp_to_be_added) |> 
  mutate(`expenditure_1994-1999_budget` = ifelse(`expenditure_1994-1999_budget` == 0,
                                                 NA, `expenditure_1994-1999_budget`))
```

```{r}
# Now the '95 enlargement is fine
NUTS_1994 <- funds |> filter(Year == 1994) |> pull(NUTS2_ID) |> unique()
NUTS_1995 <- funds |> filter(Year == 1995) |> pull(NUTS2_ID) |> unique()
missing_1994 <- setdiff(NUTS_1995, NUTS_1994)
missing_1994
# Only regions from the countries that joined in '95 make up the difference
```

```{r}
# From the 2000s regions of the 2004 enlargement appear
NUTS_1999 <- funds |> filter(Year == 1999) |> pull(NUTS2_ID) |> unique()
NUTS_2000 <- funds |> filter(Year == 2000) |> pull(NUTS2_ID) |> unique()
missing_2000 <- setdiff(NUTS_2000, NUTS_1999)
missing_2000
NUTS_2001 <- funds |> filter(Year == 2001) |> pull(NUTS2_ID) |> unique()
missing_2001 <- setdiff(NUTS_2001, NUTS_2000)
missing_2001
NUTS_2002 <- funds |> filter(Year == 2002) |> pull(NUTS2_ID) |> unique()
missing_2002 <- setdiff(NUTS_2002, NUTS_2001)
missing_2002

# This is the same problem as for the previous enlargement
df <- funds |>
  filter(Country %in% c("CY", "CZ", "LT", "LV", "MT", "PL", "SK", "SI", "HU", "EE") & 
           Year %in% c(2000, 2001, 2002, 2003))
funds <- funds |>
  filter(!(Country %in% c("CY", "CZ", "LT", "LV", "MT", "PL", "SK", "SI", "HU", "EE") & 
           Year %in% c(2000, 2001, 2002, 2003)))
df <- df |> 
  mutate(Year = 2004) |> 
  select(Country, NUTS2_ID, NUTS2_name, Year, `expenditure_2000-2006_budget`) |> 
  summarise(exp_to_be_added = sum(`expenditure_2000-2006_budget`, na.rm = TRUE), 
            .by = c(Country, NUTS2_ID, NUTS2_name, Year))
funds <- funds |> 
  left_join(df, by = c("Country", "NUTS2_ID", "NUTS2_name", "Year")) |> 
  mutate(`expenditure_2000-2006_budget` = 
           rowSums(across(c(`expenditure_2000-2006_budget`, exp_to_be_added)), 
                   na.rm = TRUE)) |> 
  select(-exp_to_be_added) |> 
  mutate(`expenditure_2000-2006_budget` = ifelse(`expenditure_2000-2006_budget` == 0,
                                                 NA, `expenditure_2000-2006_budget`))
```

```{r}
# Some regions do not appear for a few years, I assume they did not receive any money
NUTS_2004 <- funds |> filter(Year == 2004) |> pull(NUTS2_ID) |> unique()
NUTS_2005 <- funds |> filter(Year == 2005) |> pull(NUTS2_ID) |> unique()
missing_2005 <- setdiff(NUTS_2004, NUTS_2005)
missing_2005
NUTS_2006 <- funds |> filter(Year == 2006) |> pull(NUTS2_ID) |> unique()
missing_2006 <- setdiff(NUTS_2004, NUTS_2006)
missing_2006
missing_2005 <- funds |> 
  filter(NUTS2_ID %in% missing_2005) |> 
  filter(Year == 2004) |> 
  mutate(Year = 2005,
         "expenditure_2000-2006_budget"= 0)
funds <- funds |> 
  rbind(missing_2005) |> 
  arrange(NUTS2_ID, Year)
missing_2006 <- funds |> 
  filter(NUTS2_ID %in% missing_2006) |> 
  filter(Year == 2004) |> 
  mutate(Year = 2006,
         "expenditure_2000-2006_budget"= 0)
funds <- funds |> 
  rbind(missing_2006) |> 
  arrange(NUTS2_ID, Year)
```

```{r}
# Checking enlargement '07
NUTS_2006 <- funds |> filter(Year == 2006) |> pull(NUTS2_ID) |> unique()
NUTS_2007 <- funds |> filter(Year == 2007) |> pull(NUTS2_ID) |> unique()
missing_2006 <- setdiff(NUTS_2007, NUTS_2006)
# Croatia appears earlier than it should
missing_2006

# Again I will set all expenditure for Croatia to be in 2013
df <- funds |>
  filter(Country == "HR" & 
           Year %in% c(2007, 2008, 2009, 2010, 2011, 2012))
# Filtering them out of the main df
funds <- funds |>
  filter(!(Country == "HR" & 
           Year %in% c(2007, 2008, 2009, 2010, 2011, 2012)))
# Modifying and adding that data to the main df for year 2013
df <- df |> 
  mutate(Year = 2013) |> 
  select(Country, NUTS2_ID, NUTS2_name, Year, `expenditure_2007-2013_budget`) |> 
  summarise(exp_to_be_added = sum(`expenditure_2007-2013_budget`, na.rm = TRUE), 
            .by = c(Country, NUTS2_ID, NUTS2_name, Year))
funds <- funds |> 
  left_join(df, by = c("Country", "NUTS2_ID", "NUTS2_name", "Year")) |> 
  mutate(`expenditure_2007-2013_budget` = 
           rowSums(across(c(`expenditure_2007-2013_budget`, exp_to_be_added)), 
                   na.rm = TRUE)) |> 
  select(-exp_to_be_added) |> 
  mutate(`expenditure_2007-2013_budget` = ifelse(`expenditure_2007-2013_budget` == 0,
                                                 NA, `expenditure_2007-2013_budget`))
```

This is almost all, I should also check for what happens with Brexit but this will be done later on

```{r}
# Check BREXIT

funds |> 
  group_by(Year) |> 
  summarise(n_countries = n_distinct(Country))

# Counting the number of regions
funds |> 
  group_by(Year) |> 
  summarise(n_regions = n_distinct(NUTS2_ID))
```

Setting the NAs for all the cells that are outside of the expenditure timeframe

```{r}
# '89-'93 goes on until '98
funds |>  filter(`expenditure_1989-1993_budget` > 0) |> 
  summarise(min(Year), max(Year))
# Modifying the dataframe accordignly
funds <- funds |>
  mutate(
    `expenditure_1989-1993_budget` = case_when(
      Year >= 1989 & Year <= 1998 & is.na(`expenditure_1989-1993_budget`) ~ 0,
      Year < 1989 | Year > 1998 ~ NA,
      TRUE ~ `expenditure_1989-1993_budget`))

# '94-'99 goes on until '02
funds |>  filter(`expenditure_1994-1999_budget` > 0) |> 
  summarise(min(Year), max(Year))
# Modifying the dataframe accordignly
funds <- funds |>
  mutate(
    `expenditure_1994-1999_budget` = case_when(
      Year >= 1994 & Year <= 2002 & is.na(`expenditure_1994-1999_budget`) ~ 0,
      Year < 1994 | Year > 2002 ~ NA,
      TRUE ~ `expenditure_1994-1999_budget`))

# '00-'06 goes on until '09
funds |>  filter(`expenditure_2000-2006_budget` > 0) |> 
  summarise(min(Year), max(Year))
# Modifying the dataframe accordignly
funds <- funds |>
  mutate(
    `expenditure_2000-2006_budget` = case_when(
      Year >= 2000 & Year <= 2009 & is.na(`expenditure_2000-2006_budget`) ~ 0,
      Year < 2000 | Year > 2009 ~ NA,
      TRUE ~ `expenditure_2000-2006_budget`))

# '07-'13 goes on until '15
funds |>  filter(`expenditure_2007-2013_budget` > 0) |> 
  summarise(min(Year), max(Year))
# Modifying the dataframe accordignly
funds <- funds |>
  mutate(
    `expenditure_2007-2013_budget` = case_when(
      Year >= 2007 & Year <= 2015 & is.na(`expenditure_2007-2013_budget`) ~ 0,
      Year < 2007 | Year > 2015 ~ NA,
      TRUE ~ `expenditure_2007-2013_budget`))

# '14-'20 goes on until '22
funds |>  filter(`expenditure_2014-2020_budget` > 0) |> 
  summarise(min(Year), max(Year))
# Modifying the dataframe accordignly
funds <- funds |>
  mutate(
    `expenditure_2014-2020_budget` = case_when(
      Year >= 2014 & Year <= 2022 & is.na(`expenditure_2014-2020_budget`) ~ 0,
      Year < 2014 | Year > 2022 ~ NA,
      TRUE ~ `expenditure_2014-2020_budget`))
```

# Other data

```{r}
unemployment_raw <- read_csv("unemployment.csv")

# Selecting only relevant variables
unemployment <- unemployment_raw |> 
  select(geo, TIME_PERIOD, OBS_VALUE)

min(unemployment$TIME_PERIOD)
max(unemployment$TIME_PERIOD)

unemployment <- unemployment |> 
  # Separating region code and name
  separate_wider_delim(cols = geo, delim = ":", names = c("NUTS2_ID", "NUTS2_name")) |> 
  rename(Year = TIME_PERIOD,
         Unemployment = OBS_VALUE)
```


```{r}
unique(unemployment$NUTS2_ID) |> setdiff(nuts_funded)
# Starts with FR is due to France relabelling
# HR, HU, IE, LT, PL, SI, UK are all EU
# Starts with CH | IS | ME | MK | NO | RS | TR can be deleted

# Deleting non-EU regions
unemployment <- unemployment |> 
  filter(!grepl("^(CH|IS|ME|MK|NO|RS|TR)", NUTS2_ID))

# Mainly regions that have probably changed nuts label
unique(unemployment$NUTS2_ID) |> setdiff(nuts_funded)
```

Is this data using 2021 nuts codes?

```{r}
NUTS16_21 <- read_excel("NUTS2021.xlsx", 
    sheet = "NUTS & SR 2021", range = "A1:H1845")

NUTS_2021 <- NUTS16_21 |> 
  filter(`NUTS level` == 2) |> 
  select(`Code 2021`, `NUTS level 2`) |> 
  drop_na(`Code 2021`)

nuts_data <- unique(unemployment$NUTS2_ID) 
all_nuts <- unique(NUTS_2021$`Code 2021`)

setdiff(nuts_data, all_nuts)
# These are all regions that have been subject to changes

# HR04 discontinued with NUTS2021; split into new HR02, HR05 and HR06 - last data 2015
# HU10 discontinued with NUTS2016; split into new HU11 and HU12 - last data 2012
# IE01 & IE02 discontinued with NUTS2016 - last data 2011
# LT00 discontinued with NUTS2016; split into new LT01 and LT02 - last data 2012
# SI01 & SI02 discontinued with NUTS2013 - last data 2009
# UKI1 & UKI2 discontinued with NUTS2013 - last data 2009
# UKM2 & UKM3 discontinued with NUTS2016 - last data 2012

# Basically all the unemployment data uses nuts 2021 codes, for regions that have had some changes affecting their boundaries and thus their datapoints, data is kept for the previous region before the changes and new regions are used after the changes

# To the above it must be added the following change affecting boundaries:
# PL12 discontinued with NUTS 2016; split into new PL91 and PL92 - data for PL91 and PL92 from 2013, no old data

# And the following regions just changing the code: 
# FR24	FRB0
# FR26	FRC1
# FR43	FRC2
# FR25	FRD1
# FR23	FRD2
# FR30	FRE1
# FR22	FRE2
# FR42	FRF1
# FR21	FRF2
# FR41	FRF3
# FR51	FRG0
# FR52	FRH0
# FR61	FRI1
# FR63	FRI2
# FR53	FRI3
# FR81	FRJ1
# FR62	FRJ2
# FR72	FRK1
# FR71	FRK2
# FR82	FRL0
# FR83	FRM0
# FRA1	FRY1
# FRA2	FRY2
# FRA3	FRY3
# FRA4	FRY4
# FRA5	FRY5
# PL11	PL71
# PL33	PL72
# PL31	PL81
# PL32	PL82
# PL34	PL84
```

Checking now differences in NUTS code for unemployment dataset against the funds dataset. Probably all the changes mentioned above should pop up.

```{r}
nuts_unemployment <- unique(unemployment$NUTS2_ID)
nuts_funded <- unique(funds$NUTS2_ID)
all_nuts <- unique(NUTS_2021$`Code 2021`)

setdiff(nuts_funded, all_nuts)
# All regions subject to changes as discussed before
setdiff(nuts_funded, nuts_unemployment)
# All regions subject to name changes + PL12 for which no pre-change data is available

setdiff(all_nuts, nuts_funded)
# Most of the difference is due to the changes mentioned above, many can be fixed by simply changing the code of the region. The ones involving boundary shifts cannot be changed
# The rest of the differences are ZZ territories which are not included in my analysis
```

Updating the 2013 NUTS codes from the `funds` dataset to match their new nuts code for regions in Poland and France which only underwent code changes and no boundary shift

```{r}
funds <- funds |> 
  mutate(NUTS2_ID = case_when(
    NUTS2_ID == "FR24" ~ "FRB0",
    NUTS2_ID == "FR26" ~ "FRC1",
    NUTS2_ID == "FR43" ~ "FRC2",
    NUTS2_ID == "FR25" ~ "FRD1",
    NUTS2_ID == "FR23" ~ "FRD2",
    NUTS2_ID == "FR30" ~ "FRE1",
    NUTS2_ID == "FR22" ~ "FRE2",
    NUTS2_ID == "FR42" ~ "FRF1",
    NUTS2_ID == "FR21" ~ "FRF2",
    NUTS2_ID == "FR41" ~ "FRF3",
    NUTS2_ID == "FR51" ~ "FRG0",
    NUTS2_ID == "FR52" ~ "FRH0",
    NUTS2_ID == "FR61" ~ "FRI1",
    NUTS2_ID == "FR63" ~ "FRI2",
    NUTS2_ID == "FR53" ~ "FRI3",
    NUTS2_ID == "FR81" ~ "FRJ1",
    NUTS2_ID == "FR62" ~ "FRJ2",
    NUTS2_ID == "FR72" ~ "FRK1",
    NUTS2_ID == "FR71" ~ "FRK2",
    NUTS2_ID == "FR82" ~ "FRL0",
    NUTS2_ID == "FR83" ~ "FRM0",
    NUTS2_ID == "FRA1" ~ "FRY1",
    NUTS2_ID == "FRA2" ~ "FRY2",
    NUTS2_ID == "FRA3" ~ "FRY3",
    NUTS2_ID == "FRA4" ~ "FRY4",
    NUTS2_ID == "FRA5" ~ "FRY5",
    NUTS2_ID == "PL11" ~ "PL71",
    NUTS2_ID == "PL33" ~ "PL72",
    NUTS2_ID == "PL31" ~ "PL81",
    NUTS2_ID == "PL32" ~ "PL82",
    NUTS2_ID == "PL34" ~ "PL84",
    TRUE ~ NUTS2_ID))

# Checking if everything is fine
nuts_unemployment <- unique(unemployment$NUTS2_ID)
nuts_funded <- unique(funds$NUTS2_ID)
all_nuts <- unique(NUTS_2021$`Code 2021`)

setdiff(nuts_funded, all_nuts)
# Only the regions with boundary changes appear, perfect.

setdiff(all_nuts, nuts_funded)
# All the regions coming from shifts plus FRY5 which is Mayotte and for which there is no data in the funds dataset
```

All seems fine for now we can proceed with merging

```{r}
data <- funds |> 
  left_join(unemployment, by = c("NUTS2_ID", "Year")) |> 
  filter(Year >= 1999 & Year <= 2022) |> 
  select(-`expenditure_1989-1993_budget`)

funds |> 
  anti_join(unemployment, by = c("NUTS2_ID", "Year")) |> 
  filter(Year >= 1999)
# Still loosing a lot of data because of pre 2010 nuts code changes

# NEED TO LOOK INTO THIS LATER IF I STICK TO THIS DATA

# names are all the same it is worth not carrying them forward if possible to trace them back using nuts data
check <- data |> 
  mutate(name_check_equal = ifelse(NUTS2_name.x == NUTS2_name.y, TRUE, FALSE)) |> 
  filter(name_check_equal==FALSE)
```

```{r}
gdp_raw <- read_csv("gdp.csv")
gdp <- gdp_raw |> 
  filter(unit == "Purchasing power standard (PPS, EU27 from 2020), per inhabitant")

gdp <- gdp |> 
  select(geo, TIME_PERIOD, OBS_VALUE) |> 
  rename(NUTS2_name = geo,
         Year = TIME_PERIOD,
         GDP = OBS_VALUE)

min(gdp$Year)
max(gdp$Year)

data <- data |> 
  left_join(gdp, by = c("NUTS2_name.y" = "NUTS2_name", "Year" = "Year")) |> 
  filter(Year >= 2000 & Year <= 2022)
```


```{r}
population_raw <- read_csv("population.csv")

population <- population_raw |> 
  select(geo, TIME_PERIOD, OBS_VALUE)

min(population$TIME_PERIOD)
max(population$TIME_PERIOD)

population <- population |> 
  separate_wider_delim(cols = geo, delim = ":", names = c("NUTS2_ID", "NUTS2_name")) |> 
  rename(Year = TIME_PERIOD,
         Population = OBS_VALUE)

unique(population$NUTS2_ID) |> setdiff(nuts_funded)
# Starts with FR is due to France relabelling
# HR, HU, IE, LT, NL, PL, PT, SI, UK are all EU
# Starts with AL | CH | IS | LI | ME | MK | NO | RS | TR can be deleted
population <- population |> 
  filter(!grepl("^(AL|CH|IS|LI|ME|MK|NO|RS|TR)", NUTS2_ID))

# Mainly regions that have probably changed nuts label
unique(population$NUTS2_ID) |> setdiff(nuts_funded)

data <- data |> 
  left_join(population, by = c("NUTS2_ID", "Year")) |> 
  filter(Year >= 2000 & Year <= 2022) 
```


```{r}
education_raw <- read_csv("education.csv")

education <- education_raw |> 
  select(geo, TIME_PERIOD, OBS_VALUE) |> 
  rename(NUTS2_name = geo,
         Year = TIME_PERIOD,
         Education = OBS_VALUE)

min(education$Year)
max(education$Year)

data <- data |> 
  left_join(education, by = c("NUTS2_name.y" = "NUTS2_name", "Year" = "Year")) |> 
  filter(Year >= 2000 & Year <= 2022)
```

```{r}
gfcf_raw <- read_csv("gfcf.csv")
gfcf <- gfcf_raw |> 
  filter(currency == "Million euro")

gfcf <- gfcf |> 
  select(geo, TIME_PERIOD, OBS_VALUE) |> 
  rename(NUTS2_name = geo,
         Year = TIME_PERIOD,
         GFCF = OBS_VALUE)

min(gfcf$Year)
max(gfcf$Year)

data <- data |> 
  left_join(gfcf, by = c("NUTS2_name.y" = "NUTS2_name", "Year" = "Year")) |> 
  filter(Year >= 2000 & Year <= 2022)
```

# Getting ready for regressions

```{r}
data <- data |> 
  select(-c(NUTS2_name.y, NUTS2_name)) |>
  rename(NUTS2_name = NUTS2_name.x)

data <- data |> 
  filter(!is.na(Unemployment) & 
         !is.na(GDP) & 
         !is.na(Population) & 
         !is.na(Education) & 
         !is.na(GFCF))

data_gr <- data |> 
  arrange(NUTS2_ID, Year) |> 
  group_by(NUTS2_ID) |> 
  mutate(
    Year_lag = lag(Year),
    Unemployment = case_when(
      Year_lag == Year - 1 ~ (Unemployment - lag(Unemployment)) / lag(Unemployment) * 100,
      TRUE ~ NA)) |> 
  select(-Year_lag) |> 
  ungroup()

data_gr <- data_gr |>
  filter(!is.na(Unemployment))

# Expenditure per capita
data_gr <- data_gr |> 
  mutate(across(starts_with("expenditure"), ~ .x/Population))
data <- data |> 
  mutate(across(starts_with("expenditure"), ~ .x/Population))
```

```{r}
dim(data)
dim(data_gr)

plot_missing(data)
plot_missing(data_gr)
```

```{r}
# List of dataframes, one per year
list_data_gr <- split(data_gr, data_gr$Year)

#  Removing columns with all NAs (i.e. Keeping only the relevant budget cycle columns for each year)
list_data_gr_cleaned <- map(list_data_gr, ~ .x[, colSums(!is.na(.x)) > 0])

# How many regions per year
lapply(list_data_gr_cleaned, dim)

# Keeping only the numeric variables for regression 
list_data_gr_cleaned <- map(list_data_gr_cleaned, ~ 
  .x |> 
    select(where(is.numeric)) |> 
    select(-Year))
```

```{r}
list_data <- split(data, data$Year)
list_data_cleaned <- map(list_data, ~ .x[, colSums(!is.na(.x)) > 0])
lapply(list_data_cleaned, dim)
list_data_cleaned <- map(list_data_cleaned, ~ 
  .x |> 
    select(where(is.numeric)) |> 
    select(-Year))
```


# Regression

1) Model using growth rate unemployment

```{r}
regression_gr <- map(list_data_gr_cleaned, ~ lm(Unemployment ~ ., data = .x))

rsquared <- map_dbl(regression_gr, ~ summary(.x)$r.squared)
gr <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)

coefficients <- map_dfr(regression_gr, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(regression_gr, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

gr <- gr |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("`expenditure_2007-2013_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("`expenditure_2014-2020_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_Population", .after = "Population") |> 
  relocate("p.value_Education", .after = "Education") |>
  relocate("p.value_GDP", .after = "GDP") |>
  relocate("p.value_GFCF", .after = "GFCF") |> 
  relocate("p.value_`expenditure_1994-1999_budget`", .after = "`expenditure_1994-1999_budget`") |> 
  relocate("p.value_`expenditure_2000-2006_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("p.value_`expenditure_2007-2013_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_`expenditure_2014-2020_budget`", .after = "`expenditure_2014-2020_budget`")

# Growth rate of unemployment should be negative
# Expected coefficients
# expenditure -> negative
# GDP -> negative
# Education -> negative
# GFCF -> negative
# Population -> positive
```

2) Model using absolute value instead of growth rate

```{r}
regression_ab <- map(list_data_cleaned, ~ lm(Unemployment ~ ., data = .x))

rsquared <- map_dbl(regression_ab, ~ summary(.x)$r.squared)
ab <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)

coefficients <- map_dfr(regression_ab, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(regression_ab, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

ab <- ab |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("`expenditure_2007-2013_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("`expenditure_2014-2020_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_Population", .after = "Population") |> 
  relocate("p.value_Education", .after = "Education") |>
  relocate("p.value_GDP", .after = "GDP") |>
  relocate("p.value_GFCF", .after = "GFCF") |> 
  relocate("p.value_`expenditure_1994-1999_budget`", .after = "`expenditure_1994-1999_budget`") |> 
  relocate("p.value_`expenditure_2000-2006_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("p.value_`expenditure_2007-2013_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_`expenditure_2014-2020_budget`", .after = "`expenditure_2014-2020_budget`")

# Unemployment should decrease
# Expected coefficients
# expenditure -> negative
# GDP -> negative
# Education -> negative
# GFCF -> negative
# Population -> positive
```

Growth rate has better coefficients for expenditure


3) Run a model just with the controls and check whether variables are significant and the R2 of this simple model

```{r}
# GDP
regression1 <- map(list_data_gr_cleaned, ~ lm(Unemployment ~ GDP, data = .x))
rsquared <- map_dbl(regression1, ~ summary(.x)$r.squared)
solo_gdp <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)
coefficients <- map_dfr(
  regression1,
  ~ broom::tidy(.x), 
  .id = "year") |> 
  filter(term == "GDP") |> 
  select(year, term, estimate, p.value) |>
  pivot_wider(names_from = term, values_from = estimate)
solo_gdp <- solo_gdp |> 
  left_join(coefficients, by = "year") |> 
  mutate(across(where(is.numeric), ~ round(.x, 6)))
```

```{r}
# Education
regression2 <- map(list_data_gr_cleaned, ~ lm(Unemployment ~ Education, data = .x))
rsquared <- map_dbl(regression2, ~ summary(.x)$r.squared)
solo_edu <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)
coefficients <- map_dfr(
  regression2,
  ~ broom::tidy(.x), 
  .id = "year") |> 
  filter(term == "Education") |> 
  select(year, term, estimate, p.value) |>
  pivot_wider(names_from = term, values_from = estimate)
solo_edu <- solo_edu |> 
  left_join(coefficients, by = "year") |> 
  mutate(across(where(is.numeric), ~ round(.x, 6)))
```

```{r}
# Investment
regression3 <- map(list_data_gr_cleaned, ~ lm(Unemployment ~ GFCF, data = .x))
rsquared <- map_dbl(regression3, ~ summary(.x)$r.squared)
solo_inv <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)
coefficients <- map_dfr(
  regression3,
  ~ broom::tidy(.x), 
  .id = "year") |> 
  filter(term == "GFCF") |> 
  select(year, term, estimate, p.value) |>
  pivot_wider(names_from = term, values_from = estimate)
solo_inv <- solo_inv |> 
  left_join(coefficients, by = "year") |> 
  mutate(across(where(is.numeric), ~ round(.x, 6)))
```

```{r}
# Population
regression4 <- map(list_data_gr_cleaned, ~ lm(Unemployment ~ Population, data = .x))
rsquared <- map_dbl(regression4, ~ summary(.x)$r.squared)
solo_pop <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)
coefficients <- map_dfr(
  regression4,
  ~ broom::tidy(.x), 
  .id = "year") |> 
  filter(term == "Population") |> 
  select(year, term, estimate, p.value) |>
  pivot_wider(names_from = term, values_from = estimate)
solo_pop <- solo_pop |> 
  left_join(coefficients, by = "year") |> 
  mutate(across(where(is.numeric), ~ round(.x, 6)))
```

```{r}
# All controls
regression5 <- map(list_data_gr_cleaned, ~ lm(Unemployment ~ Population + Education + GDP + GFCF, 
                                              data = .x))
rsquared <- map_dbl(regression5, ~ summary(.x)$r.squared)
solo_controls <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)
coefficients <- map_dfr(
  regression5,
  ~ broom::tidy(.x), 
  .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(
  regression5,
  ~ broom::tidy(.x), 
  .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

solo_controls <- solo_controls |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("p.value_Population", .after = "Population") |> 
  relocate("p.value_Education", .after = "Education") |>
  relocate("p.value_GDP", .after = "GDP") |>
  relocate("p.value_GFCF", .after = "GFCF")
```

None is constantly significant


4) Run model only with expenditure to check if they have the correct sign and whether they are insignificant (in the case they do not have the correct sign)

```{r}
no_controls <- map(list_data_gr_cleaned, ~ .x |>
                     select(-Population, -Education, -GFCF, -GDP))

regression_nc <- map(no_controls, ~ lm(Unemployment ~ ., data = .x))

rsquared <- map_dbl(regression_nc, ~ summary(.x)$r.squared)
nc <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)

coefficients <- map_dfr(
  regression_nc, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(regression_nc, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

nc <- nc |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("p.value_`expenditure_1994-1999_budget`", .after = "`expenditure_1994-1999_budget`") |> 
  relocate("p.value_`expenditure_2000-2006_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("p.value_`expenditure_2007-2013_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_`expenditure_2014-2020_budget`", .after = "`expenditure_2014-2020_budget`")
```

Does not change


5) Take out population to see if the model improves

```{r}
no_pop <- map(list_data_gr_cleaned, ~ .x |>
                select(-Population))

regression_np <- map(no_pop, ~ lm(Unemployment ~ ., data = .x))

rsquared <- map_dbl(regression_np, ~ summary(.x)$r.squared)
np <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)

coefficients <- map_dfr(regression_np, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(regression_np, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

np <- np |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("`expenditure_2007-2013_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("`expenditure_2014-2020_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_Education", .after = "Education") |>
  relocate("p.value_GDP", .after = "GDP") |>
  relocate("p.value_GFCF", .after = "GFCF") |> 
  relocate("p.value_`expenditure_1994-1999_budget`", .after = "`expenditure_1994-1999_budget`") |> 
  relocate("p.value_`expenditure_2000-2006_budget`", .after = "`expenditure_2000-2006_budget`") |>
  relocate("p.value_`expenditure_2007-2013_budget`", .after = "`expenditure_2007-2013_budget`") |>
  relocate("p.value_`expenditure_2014-2020_budget`", .after = "`expenditure_2014-2020_budget`")
```

Does not change (makes it a bit worse)


6) Try to use the lag version of the independent

```{r}
# Lagging
lagged_data <- data_gr |> 
  group_by(NUTS2_ID) %>%
  mutate(across(starts_with("expenditure"), 
                ~lag(., 1),
                .names = "{.col}_lag1")) |> 
  mutate(across(starts_with("expenditure") & !ends_with("lag1"),
                ~lag(., 3),
                .names = "{.col}_lag3")) |>
  ungroup()
```

```{r}
# Only lag-1
lagged_1 <- lagged_data |> 
  select(-c(`expenditure_1994-1999_budget`, 
            `expenditure_2000-2006_budget`, 
            `expenditure_2007-2013_budget`, 
            `expenditure_2014-2020_budget`,
            `expenditure_1994-1999_budget_lag3`, 
            `expenditure_2000-2006_budget_lag3`, 
            `expenditure_2007-2013_budget_lag3`, 
            `expenditure_2014-2020_budget_lag3`))

list_lag_data <- split(lagged_1, lagged_1$Year)
list_lag_data_cleaned <- map(list_lag_data, ~ .x[, colSums(!is.na(.x)) > 0])
list_lag_data_cleaned <- map(list_lag_data_cleaned, ~ 
  .x |> 
    select(where(is.numeric)) |> 
    select(-Year))
```

```{r}
regression_lag <- map(list_lag_data_cleaned, ~ lm(Unemployment ~ ., data = .x))

rsquared <- map_dbl(regression_lag, ~ summary(.x)$r.squared)
lag_1 <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)

coefficients <- map_dfr(regression_lag, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(regression_lag, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

lag_1 <- lag_1 |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("`expenditure_2007-2013_budget_lag1`", .after = "`expenditure_2000-2006_budget_lag1`") |>
  relocate("`expenditure_2014-2020_budget_lag1`", .after = "`expenditure_2007-2013_budget_lag1`") |>
  relocate("p.value_Population", .after = "Population") |> 
  relocate("p.value_Education", .after = "Education") |>
  relocate("p.value_GDP", .after = "GDP") |>
  relocate("p.value_GFCF", .after = "GFCF") |> 
  relocate("p.value_`expenditure_1994-1999_budget_lag1`", .after = "`expenditure_1994-1999_budget_lag1`") |> 
  relocate("p.value_`expenditure_2000-2006_budget_lag1`", .after = "`expenditure_2000-2006_budget_lag1`") |>
  relocate("p.value_`expenditure_2007-2013_budget_lag1`", .after = "`expenditure_2007-2013_budget_lag1`") |>
  relocate("p.value_`expenditure_2014-2020_budget_lag1`", .after = "`expenditure_2014-2020_budget_lag1`")
```



```{r}
# Only lag-3
lagged_3 <- lagged_data |> 
  select(-c(`expenditure_1994-1999_budget`, 
            `expenditure_2000-2006_budget`, 
            `expenditure_2007-2013_budget`, 
            `expenditure_2014-2020_budget`,
            `expenditure_1994-1999_budget_lag1`, 
            `expenditure_2000-2006_budget_lag1`, 
            `expenditure_2007-2013_budget_lag1`, 
            `expenditure_2014-2020_budget_lag1`))

list_lag_data <- split(lagged_3, lagged_3$Year)
list_lag_data_cleaned <- map(list_lag_data, ~ .x[, colSums(!is.na(.x)) > 0])
list_lag_data_cleaned <- map(list_lag_data_cleaned, ~ 
  .x |> 
    select(where(is.numeric)) |> 
    select(-Year))
```

```{r}
regression_lag <- map(list_lag_data_cleaned, ~ lm(Unemployment ~ ., data = .x))

rsquared <- map_dbl(regression_lag, ~ summary(.x)$r.squared)
lag_3 <- tibble(
  year = names(rsquared),
  r_squared = as.numeric(rsquared)
)

coefficients <- map_dfr(regression_lag, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, estimate) |>
  pivot_wider(names_from = term, values_from = estimate)
pvals <- map_dfr(regression_lag, ~ broom::tidy(.x), .id = "year") |> 
  filter(term != "(Intercept)") |> 
  select(year, term, p.value) |> 
  pivot_wider(names_from = term, values_from = p.value, names_prefix = "p.value_")

lag_3 <- lag_3 |> 
  left_join(coefficients, by = "year") |> 
  left_join(pvals, by = "year") |>
  mutate(across(where(is.numeric), ~ round(.x, 6))) |> 
  relocate("`expenditure_2007-2013_budget_lag3`", .after = "`expenditure_2000-2006_budget_lag3`") |>
  relocate("`expenditure_2014-2020_budget_lag3`", .after = "`expenditure_2007-2013_budget_lag3`") |>
  relocate("p.value_Population", .after = "Population") |> 
  relocate("p.value_Education", .after = "Education") |>
  relocate("p.value_GDP", .after = "GDP") |>
  relocate("p.value_GFCF", .after = "GFCF") |> 
  relocate("p.value_`expenditure_1994-1999_budget_lag3`", .after = "`expenditure_1994-1999_budget_lag3`") |> 
  relocate("p.value_`expenditure_2000-2006_budget_lag3`", .after = "`expenditure_2000-2006_budget_lag3`") |>
  relocate("p.value_`expenditure_2007-2013_budget_lag3`", .after = "`expenditure_2007-2013_budget_lag3`") |>
  relocate("p.value_`expenditure_2014-2020_budget_lag3`", .after = "`expenditure_2014-2020_budget_lag3`")
```

Population always out

Look for a trade variable (export-import)

Lag the dependent variable (growth rate of unemployment)

Use GDP instead of unemployment



Look for the years that are significant (high R2) and try to understand why R2 is high in those years (look at p-values of coefficients)

In general look at the p-values of the expenditure and understand when and maybe why they are significant rather than not




Look at papers to see how they model unemployment



Using absolute value of unemployment and the lag-1 version of it, plus lagged independent?

Looking at poverty rates instead?

```{r}

```




If you have a good model include one by one threshold info and expenditure


# Available variables

```{r}
library(restatapi)
toc <- search_eurostat_toc("NUTS 2")


```

